---
title: "lkp_vars"
author: "Javed Mohib"
format: html
editor: visual
---

## **Introduction**

The **`lkp_var`** function is used to look up the definition, values, and labels of a QILT variable. This is particularly useful when working with survey data where it is important to understand the meaning and possible values of each variable.

# **Usage**

The **`lkp_var`** function takes a single argument, the QILT variable name, and returns a list of two elements:

-   **`Variable`**: A tibble with the variable name, definition, and format.

-   **`Value`**: A tibble with the possible values and their corresponding labels.

# **Example**

Here are a few examples of how to use the **`lkp_var`** function:

```{r}
# Look up the definition and values for the variable "e329"
var_info <- lkp_var("e329")

# Access the definition of the variable
var_info$Variable
#> # A tibble: 1 x 3
#>   variable  label                  format      
#>   <chr>     <chr>                  <chr>       
#> 1 e329      Field of study         categorical

# Access the possible values and their labels
var_info$Value
#> # A tibble: 10 x 2
#>    value label                                                                                                          
#>    <chr> <chr>                                                                                                          
#>  1 01    Architecture and Building                                                                                      
#>  2 02    Business and Management                                                                                         
#>  3 03    Education                                                                                                        
#>  4 04    Engineering and Related Technologies                                                                             
#>  5 05    Health                                                                                                           
#>  6 06    Information and Communication Technologies                                                                       
#>  7 07    Law and Legal Studies                                                                                            
#>  8 08    Science                                                                                                          
#>  9 09    Society and Culture                                                                                             
#> 10 10    Other                                                                                                            

```

```{r}
# Look up the definition and values for the variable "en1"
var_info <- lkp_var("en1")

# Access the definition of the variable
var_info$Variable
#> # A tibble: 1 x 3
#>   variable  `Variable Definition` format 
#>   <chr>     <chr>                 <chr>  
#> 1 en1      English proficiency    categorical

# Access the possible values and their labels
var_info$Value
#> # A tibble: 5 x 2
#>   value label                               
#>   <chr> <chr>                               
#> 1 01    Non-English speaking background    
#> 2 02    English-speaking background only   
#> 3 03    Both English and non-English       
#> 4 04    Not stated/inadequately described 
#> 5 99    Not applicable                     

```

# **Conclusion**

The **`lkp_var`** function is a useful tool for exploring the meaning and values of QILT variables. Whether you are working with survey data or just need a quick reference, this function can help you quickly get the information you need.
